Factors affecting reliablity of state-space age-structured assessment models

### 2023-06-02 Project_0/paper/paper.Rmd
saving work

@@

@@

>>>>

Convergence results can be useful for understanding how bad convergence in applications to real data might direct the practitioner to which alternative random effects configurations is be more appropriate. The type of convergence that we might use as a diagnostic is important. And what rule of thumb we use for certain criteria e.g. 1e-6? large SEs/CVs?

@@

Summary statitics

Bias

Mohn's rho

marginal AIC

convergence types: 
1) whether the optimization completed
2) nlminb convergence flag = 0
3) max abs gradient < 1e-6
4) No NAs for SE of fixed effects returned from TMB::sdreport
5) No SE NAs AND no SE > 100

@@

Probability of convergence was better for models that assumed the correct source of process error, assumed M was known, and did not assume stock-recruit relationships.
